State of the Practice of Lattice Boltzmann Method Software Development

### 2021-07-19 StateOfPractice/Peter-Notes/Report/Report.tex
added note on Musubi LBM package to LBM Report
fixed note on Musubi LBM package to LBM Report
added second cover page LBM report

@@

The candidate software was found through search engine queries targeting authoritative lists of software. We found LBM software listed on the websites GitHub and swMATH, as well as through articles found in scholarly journals and databases.

>>>>

\newpage
\thispagestyle{empty}

\noindent\textbf{TITLE:} State of The Practice for Lattice Boltzmann Method Software

\noindent\textbf{DEGREE:} Master of Engineering (Computing and Software)

\noindent\textbf{INSTITUTION:} McMaster University

\noindent\textbf{AUTHOR:} Peter Michalski

\noindent\textbf{SUPERVISOR:} Dr. Spencer Smith and Dr. Jacques Carette

\noindent\textbf{NUMBER OF PAGES:} 119

@@

The candidate software was found through search engine queries targeting authoritative lists of software. We found LBM software listed on the websites GitHub and swMATH, as well as through articles found in scholarly journals and databases. Software packages that are not on the authoritative lists that we used were not assessed. Packages that fit our criteria but were found after data collection and analysis was conducted, such as Musubi, will need to be added to future SOP assessments.
